Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-08 draft.tex
add more figures in repo

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

\newcommand{\TODO}[1]{\hl{TODO: #1}}
\newcommand{\NOTE}[1]{\hl{NOTE: #1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}

@@

 \TODO{Here will talk about network configuration, such as network scale, link bandwidth etc. }\\

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}%
   \caption{Network Traffic. \TODO{More explanation to be added for this figure}}
   \label{fig:wkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}%
   \caption{Network Channel Busy Time. \TODO{More explanation to be added for this figure}}
   \label{fig:wkld-network-stime}
\end{figure*}

@@

Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations. MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing. However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.  \TODO{More explanation about contiguous placement and minimal routing here}

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG. \TODO{More explanation about contiguous placement and minimal routing}

CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing. \TODO{More explanation about contiguous placement and minimal routing}

@@

The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}. The ``bully" become the ``bullyee". The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration. The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}. The extra traffic come from sAMG, that been redirected by adaptive routing. \TODO{More explanation about contiguous placement and minimal routing}.

@@

\NOTE{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }

>>>>

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig
\usepackage{verbatim}
\usepackage{soul}
\usepackage{xcolor}
\newcommand{\TODO}[1]{\hl{TODO: #1}}
\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}

@@

\TODO{xxx}
\NOTE{yyy}
Here will talk about network configuration, such as network scale, link bandwidth etc.\\

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}%
   \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
   \label{fig:wkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}%
   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
   \label{fig:wkld-network-stime}
\end{figure*}

@@

Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations. MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing. However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.  \textbf{More explanation about contiguous placement and minimal routing here}

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG. \textbf{More explanation about contiguous placement and minimal routing}

CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing. \textbf{More explanation about contiguous placement and minimal routing}

@@

The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}. The ``bully" become the ``bullyee". The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration. The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}. The extra traffic come from sAMG, that been redirected by adaptive routing. \textbf{More explanation about contiguous placement and minimal routing}.

@@

\textbf{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
